\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-24 paper.tex
Added Mathieu and Aurelie to authors

\author{Rachid Alami and Séverin Lemaignan}

\address{
CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, F-31400 Toulouse, France\\
{\tt severin.lemaignan@laas.fr}, {\tt rachid.alami@laas.fr}
}

>>>>

\author{Rachid Alami, Séverin Lemaignan, Aurélie Clodic, Mathieu Warnier}

\address{
CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, F-31400 Toulouse, France\\
{\tt firstname.lastname@laas.fr}
}
